Supplement

### 2023-05-15 paper/supplement.Rmd
attempts were made

```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) 
}

@@

>>>>

# Forest plot

```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes. Original effect sizes are open dots, replication are closed dots. Coloring indicates subjective replication score, and p-original values are listed on the left side. "}

d |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  mutate(numpredInt=ifelse(predInt,1,0)) |> 
  ggplot(aes(y=reorder(target_lastauthor_year,target_d_calc, mean), color=as.factor(sub_rep)))+
    geom_vline(xintercept=0, linetype=3)+
  geom_point(aes(x=target_d_calc, shape="original"))+
  geom_point(aes(x=rep_d_calc, shape="replication"))+
  geom_segment(aes(x=target_d_calc, xend=rep_d_calc, y=target_lastauthor_year, yend=target_lastauthor_year))+
  scale_shape_manual(values=c("original"=21,"replication"=19), name=NULL)+
  coord_cartesian(xlim=c(-1.5,3.5))+
  geom_text(aes(x=-1.4, label=round(p_orig,3)), color="black", size=3, hjust=0, show.legend = F)+
  scale_color_viridis(discrete=T, direction = 1, 
                      name = "Subjective\nReplication\nSuccess\n")+theme_classic()+
  labs(x="Standardized Effect Size")+
  theme(axis.ticks.y=element_blank(), axis.title.y=element_blank())
```

# Additional model results
```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) 
}

@@

# tau**2  sensitivity analysis is a mess

```{r, include=F, echo=F}
# library(Replicate)
# do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
#     return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
#   }
#   return(NA)
# }
# 
# do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
#     yio=target_ES
#     vio=target_SE**2
#     yir=rep_ES
#     vir=rep_SE**2
#     t2=.21
#     pooled.SE = sqrt(vio + vir + t2)
#     PILo.sens = yio - qnorm(0.975) * pooled.SE
#     PIHi.sens = yio + qnorm(0.975) * pooled.SE
#     PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
#     return(PIinside.sens)
#   }
#   return(NA)
# }
# do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)){
#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
#   }
#   return(NA)
# }
# 
# do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
#   if(!is.na(target_ES)&!is.na(rep_ES)){
#     return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21, rep_SE**2))
#   }
#   return(NA)
# }
# check_sens <- d |> filter(include=="stats") |> 
#   mutate(sens_target_d=target_d_calc,
#          sens_target_se=target_SE*target_d_calc/target_ES,
#          sens_target_se2=4/target_N+target_d_calc**2/(2*target_N),
#          sens_rep_d=rep_d_calc,
#          sens_rep_se=rep_SE*rep_d_calc/rep_ES,
#          sens_target_se2=4/replication_N+rep_d_calc**2/(2*replication_N)) |> 
#   
#   rowwise() |> 
#   mutate(predInt2 = do_pred_int(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          p_orig2 = do_p_orig(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          predIntSens=do_pred_int_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se),
#          p_origSens=do_p_orig_sens(sens_target_d, sens_target_se, sens_rep_d, sens_rep_se))
# 
# 
# check_sens |> select(starts_with("sens"))
# check_sens |> #select(predInt, predInt2, predIntSens, p_orig, p_orig2, p_origSens) |> 
#   filter(signif(p_orig,2)!=signif(p_orig2,2)) |> View()
# 
# check_sens |> group_by(predIntSens) |> tally()
# check_sens |> group_by(predInt2) |> tally()
# check_sens |> group_by(predInt) |> tally()
# 
# check_sens |> ungroup() |> summarize(m=median(p_origSens))
# check_sens |> ungroup() |> summarize(m=median(p_orig2))
# check_sens |> ungroup() |> summarize(m=median(p_orig))
# 
# 
# check_sens |> mutate(r1=sens_target_d/target_ES, r2=sens_target_se/target_SE, r3=sens_rep_d/rep_ES, r4=sens_rep_se/rep_SE) |> select(r1,r2,r3,r4)
# 
# d |> select(replication_raw_stat, target_raw_stat, include, sensitivity) |> View()
```
